Comparison ANOVAS stand features

### 2018-01-24 analysis/analysis_KW_stand_features.Rmd
update kw

compe_sel <- compe %>% dplyr::select(ba, std, site)
```

@@

# Competence 
kw_ba <- comparaKW(compe_sel, 'ba')
kw_std <- comparaKW(compe_sel, 'std')
```

@@

variables <- c('ft_dn', 'ft_h', 'all_dn', 'all_h', 'ba', 'std')

@@

variables <- c('ft_dn', 'ft_h', 'all_dn', 'all_h', 'ba', 'std') 
output_letras <- c()

>>>>

# Seleccionamos: 
# * distance independet: BA, Stand Densisty (std) 
# * distance dependent: Site ratio proportional to distance (srd); as in Gea2014 Foreco 320:70 & Lorimer

compe_sel <- compe %>% dplyr::select(ba, std, srd, pd, site)
```

@@

# Competence 
kw_ba <- comparaKW(compe_sel, 'ba')
kw_std <- comparaKW(compe_sel, 'std')
kw_srd <- comparaKW(compe_sel, 'srd')
kw_pd <- comparaKW(compe_sel, 'pd')
```

@@

variables <- c('ft_dn', 'ft_h', 'all_dn', 'all_h', 'ba', 'std', 'srd', 'pd')

@@

variables <- c('ft_dn', 'ft_h', 'all_dn', 'all_h', 'ba', 'std', 'srd', 'pd')
output_letras <- c()
